\section{Future Work \& Conclusion}

%\begin{itemize}
%	\item Summarize your thoughts and state your final conclusion about the work you have performed.
%	\item Describe possible future work in the field that is related to you work.
%	\item Detail improvements that could be done to your work in a following project.
%	\item Identify the importance of your work and create an arch to the related work and problem defined in the previous chapters.
%\end{itemize}
In this paper, we introduced an appealing application that helps coaches to estimate their swimmers' performances. However, the underlying machine learning model does not achieve the results we hoped. One reason for this is that we focus on non-professional swimmers; thus, their performance is less constant and therefore, less predictable. Nevertheless, the coaches of these swimmers need the most assistance; thus, a reliable prediction model is of high interest. A possible improvement could be to include more data, especially for the slower 50m times to find a correlation in our data, or use data augmentation to generate more samples from the existing data.\\
Another problem is that the swimmer's performance changes within a season. In our approach, we use an age representation based on the age group of the swimmer instead of his actual age. Therefore, it would be better to include the swimmer's age in month and, more importantly, the information at which point in the season the competition took place.\\
As the related work suggests, the swimmer's anthropometry is of high importance for his performance. Therefore, it would be good to include the height or flexibility in our records. We are currently working on a different approach that includes information about the training status of the swimmer. Therefore, we collect data about the four weeks before the respective competition. This data includes the total amount of training in kilometres as well as the intensity of the training sessions, i.e. the amount of training in the aerobic area or the number of technique sessions. The first results are already promising. However, for this approach, it is indispensable to work together with a group of swimmers as the needed data is not publicly available. \\
To get a first evaluation of our approach, we had to make some constraints. If we find a good data representation to predict results, we can enlarge our predictions to different strokes and distances, as well as include times swam in a 50m pool.